---
title: "Reading data from the web"
author: Heidi Lumish
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## String vectors

```{r}
string_vec = c("my", "name", "is", "heidi")

str_detect(string_vec, "m")
str_detect(string_vec, "heidi")
str_replace(string_vec, "heidi", "Heidi")
str_replace(string_vec, "e", "This is an uppercase E")
```

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```

```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )

str_detect(string_vec, "bush")
str_detect(string_vec, "Bush")
str_detect(string_vec,"[Bb]ush")
```

Look for anything that starts with a number followed by letters
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```

Look for 7 followed by anything then 11 (but not 711)
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
str_detect(string_vec, "711")
```

Look for the open bracket symbol
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

## Why factors are weird

Here we show how you can re-level a factor variable
```{r}
factor_vec = factor(c("male", "male", "female", "female"))

as.numeric(factor_vec)

factor_vec = fct_relevel(factor_vec, "male")

as.numeric(factor_vec)
```

## NSDUH

Remember that slice takes away the first row

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

table_marj =
  read_html(nsduh_url) %>% 
  html_table() %>% 
  first() %>% 
  slice(-1) %>% view()
```

Let's clean this up!

The -11 counts backwards from the end to decide where to split
```{r}
table_marj %>% 
  select(-contains("P Value")) %>% 
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to = "percent") %>% 
  separate(age_year, into = c("age", "year"), -11)
```

Here we can split based on the open parentheses
Then we remove the letters from the percent column
Create a data frame
```{r}
marj_df =
  table_marj %>% 
  select(-contains("P Value")) %>% 
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to = "percent") %>% 
  separate(age_year, into = c("age", "year"), "\\(") %>% 
  mutate(
    year = str_replace(year, "\\)", ""), 
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)
  ) %>% 
  filter(!State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West"))
```

Do dataframe stuff!

```{r}
marj_df %>% 
  filter(age == "12-17") %>% 
  ggplot(aes(x = State, y = percent, color = year)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

fct_reorder allows you to order one variable according to another variable
```{r}
marj_df %>% 
  filter(age == "12-17") %>% 
  mutate(
    State = fct_reorder(State, percent)
  ) %>% 
  ggplot(aes(x = State, y = percent, color = year)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Restaurant Inspections

```{r}
data("rest_inspec")

rest_inspec %>% 
  slice(1:100)
```

Look at data overview
```{r}
rest_inspec %>%
  group_by(boro, grade) %>% 
  summarize(count = n())

rest_inspec %>%
  janitor::tabyl(boro, grade)
```

```{r}
rest_inspec =
  rest_inspec %>% 
  filter(
    str_detect(grade, "[ABC]"),
    !(boro == "Missing")
  ) %>% 
  mutate(boro = str_to_title(boro))
  
```

Search for pizza places, need to make it insensitive to case to capture all inspections
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "Pizza"))%>%
  janitor::tabyl(boro, grade)

rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]"))%>%
  janitor::tabyl(boro, grade)
```

infreq puts in order by frequency
```{r}
rest_inspec%>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]"))%>%
  ggplot(aes(x = boro, fill = grade)) +
  geom_bar()

rest_inspec%>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]"))%>%
  mutate(
    boro = fct_infreq(boro)
  ) %>% 
  ggplot(aes(x = boro, fill = grade)) +
  geom_bar()
```

What about changing a label...

str_replace vs. fct_recode
```{r}
rest_inspec%>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]"))%>%
  mutate(
    boro = fct_infreq(boro),
    boro = str_replace(boro, "Manhattan", "The City")
  ) %>% 
  ggplot(aes(x = boro, fill = grade)) +
  geom_bar()

rest_inspec%>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]"))%>%
  mutate(
    boro = fct_infreq(boro),
    boro = fct_recode(boro, "The City" = "Manhattan")
  ) %>% 
  ggplot(aes(x = boro, fill = grade)) +
  geom_bar()
```



